Political Support in the United States

### 2024-03-17 paper/paper.qmd
Update paper.qmd

Throughout the paper, the data utilized for analysis, including both survey and census data, measurements, is in Section 2. Following that, Section 3 introduces the model designed to generalize patterns and forecast election outcomes. It will talk about how the model is set up and model justification. In Section 4, I will talk about the predicted results derived from the model, this includes the result of the model. Lastly, Section 5 contains more detailed results in a broader context and addresses weaknesses of this paper as well as the future explorations. This paper uses the programming language R (R Core Team 2022). The analysis, the model and the visualizations use the following packages: ipumsr (Greg Freedman Ellis, Derek Burk, and Finn Roberts 2024), dplyr (Wickham et al. 2023), readr (Wickham, Hester, and Bryan 2024), tidyr (Wickham, Vaughan, and Girlich 2024), arrow (Richardson et al. 2024), ggplot2 (Wickham 2016), knitr (Xie 2014), statebins (Rudis 2020), modelsi (Arel-Bundock 2022), broom (Robinson, Hayes, and Couch 2023), here (Müller 2020), and kableExt
2024).

@@

## Source and Methodology
The 2022 Cooperative Election Study (CES) (@main_data) involved significant data preprocessing, cleaning, and labeling efforts to ensure the quality and representativeness of the survey data. These efforts are elaborated on through descriptions of sampling methodology, matching procedures, and weighting processes as outlined in the CES Guide 2022.

## Sampling and Sampling Matching
The CES 2022 dataset is a sample of adult U.S. citizens, taken from a considerably larger population, rather than an exhaustive list of all possible cases in the target population. The sample was deliberately created to be a true reflection of the population of the United States and to capture the variations among the different legislative districts for in-depth examination in the majority of states.
Through the Internet, YouGov conducted the CES 2022 survey. 60,000 adults were interviewed between September and November 2022 (pre-election data) and November and December 2022 (post-election data) for the Common Opinion. The YouGov matching approach for random sampling was used. YouGov employed the matched random sampling method at CES among other sampling techniques. The first step in this process is to count the target population, which in the case of general population research consists of all adults. This is typically done by using an extensive survey such as the American Community Survey. The target sample is then selected at random by CES from this target population. 
However, because it is frequently impractical to make direct contact with these individuals, a matching sample is chosen from among selectable respondents who share the same characteristics as the target sample. This selection process is carried out based on a multitude of attributes available in the voter and consumer databases.

@@

```
   After downloading @dataverse, We using @get_dataframe_by_name to access the CES. We select and save the data that we are most care about, which are "votereg", "presvote20post", "race", and "gender4". "votereg" represent the voter registration status. To be more specific, whether they are registered to vote or not. "presvote20post" records the president that voter select in the election of 2020. “race" describe the voter's raical or ethnic group, and "gender4" refer to the gender of voters.
  However, when we access the raw data, there are some variables that we are not interested in. Therefore, we use the codebook to delve into the details. We only care about the voter who are registered to vote, and we are mainly focus on investigating the voter who select Biden or Trump in 2020. We found out that when the "presvote20post" is 1, then this indicates the register vote for Biden, and when it is 2 represents that the voter stand for Trump. We use @tidyverse to filter to the voters that we care about and label them with meaningful title. In addition，CES also provide the information for the gender of the voter. However, we noticed that there are four types of gender, which are man, woman, non-binary, other, and none and we are more interested in the group of man and woman. Therefore, we filter the gender by using @tidyverse. When the variable "gender" is 1, this indicates "man", but we rename all "man" to "male". When the variable "gender" is 2, it refers to "woman". We also rename all "woman" to "female". Finally, the codebook also define different "race" from 1 to 8, which are White, Black, Hispanic, Asian, Native American, Middle Eastern, Two or more races, and other. We keep all those races because we are not only interested in the major racial group, but also curious about the respond from minority group.
  To better understand the raw data, a summary table @fig-variables had been drawn in order to provide more details for each variables, explaining the variables we select. We select race and gender as the key variables that related to voter behavior. In @fig-vote, we can find the support data for both Biden and Trump based on the variables of gender and race.

## Measurements 
The collected dataset from the Cooperative Election Study (CES) offers a comprehensive view of U.S. adult citizens' electoral behaviors, political opinions, and demographic characteristics. The CES 2022 dataset, gathered through an online survey by YouGov, encompasses 60,000 instances, meticulously detailed and categorized by various factors such as election experiences, contextual data, demographic information (e.g., gender and race), political affiliations, and opinions on various policy issues. This dataset ensures a reliable representation of the population through its meticulous sampling methodology and validation processes, guaranteeing that it accurately reflects the diverse perspectives within the U.S. electorate. The dataset employs a matched random sampling methodology, with its representativeness further confirmed through a two-stage weighting process involving entropy balancing and iterative proportional fitting. Preprocessing steps, including sample matching, weighting, and vote validation, are conducted to ensure data quality and representativeness, thereby minimizing the risk of representative bias.

@@

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm, `here` package of @here and `model_summary` package of @model_summary, we use the default priors from `rstanarm`

@@

@@

From the @tbl-model-summary-tableLogistic, with the constant variable, raceAsian, the intercept is -0.462 which means that the support for Biden decreases by about 0.784 units while all other variables remain the same. The following race, Hispanic (0.354), Middle Eastern (0.535), White (0.940), Native American (1.245), Two or more races (1.372) has stronger/ increasing their support for stronger/ increasing their support for Biden; in this case, the mixed race people have the strongest support for Biden. Yet, Black (−1.030) and Other  (−0.092) decrease support for Biden by looking at the coefficients.

# Discussion {#sec-Discussion}

>>>>

Throughout the paper, the data utilized for analysis, including both survey and census data, measurements, is in {#sec-data}. Following that, {#sec-model} introduces the model designed to generalize patterns and forecast election outcomes. It will talk about how the model is set up and model justification. In {#sec-results}, I will talk about the predicted results derived from the model, this includes the result of the model. Lastly, {#sec-Discussion} contains more detailed results in a broader context and addresses weaknesses of this paper as well as the future explorations. This paper uses the programming language `R`[@citeR] . The analysis, the model and the visualizations use the following packages: `dplyr`[@dplyr],  `tidyverse`[@tidyverse], `ggplot2`[@ggplot], `knitr` [@knitr],  `here` [@here] , and `kableExtra` [@kableExtra],`modelsummary`[@model_summary], and `rstanarm`[@rstanarm].

@@

## Source and Methodology
The 2022 Cooperative Election Study (CES) [@main_data] involved significant data preprocessing, cleaning, and labeling efforts to ensure the quality and representativeness of the survey data. These efforts are elaborated on through descriptions of sampling methodology, matching procedures, and weighting processes as outlined in the CES Guide 2022.

## Sampling and Sampling Matching
The CES 2022 dataset is a sample of adult U.S. citizens, taken from a considerably larger population, rather than an exhaustive list of all possible cases in the target population. The sample was deliberately created to be a true reflection of the population of the United States and to capture the variations among the different legislative districts for in-depth examination in the majority of states.
Through the Internet, YouGov [@yougov] conducted the CES 2022 survey. 60,000 adults were interviewed between September and November 2022 (pre-election data) and November and December 2022 (post-election data) for the Common Opinion. The YouGov matching approach for random sampling was used. YouGov employed the matched random sampling method at CES among other sampling techniques. The first step in this process is to count the target population, which in the case of general population research consists of all adults. This is typically done by using an extensive survey such as the American Community Survey. The target sample is then selected at random by CES from this target population. 
However, because it is frequently impractical to make direct contact with these individuals, a matching sample is chosen from among selectable respondents who share the same characteristics as the target sample. This selection process is carried out based on a multitude of attributes available in the voter and consumer databases.

@@

```
   After downloading `dataverse` [@dataverse], We using `get_dataframe_by_name` [@get_dataframe_by_name] to access the CES. We select and save the data that we are most care about, which are `votereg`, `presvote20post`, `race`, and `gender4`. `votereg` represent the voter registration status. To be more specific, whether they are registered to vote or not. `presvote20post` records the president that voter select in the election of 2020. “race" describe the voter's raical or ethnic group, and `gender4` refer to the gender of voters.
  However, when we access the raw data, there are some variables that we are not interested in. Therefore, we use the codebook to delve into the details. We only care about the voter who are registered to vote, and we are mainly focus on investigating the voter who select Biden or Trump in 2020. We found out that when the "presvote20post" is 1, then this indicates the register vote for Biden, and when it is 2 represents that the voter stand for Trump. We use `tidyverse` [@tidyverse] to filter to the voters that we care about and label them with meaningful title. In addition，CES also provide the information for the gender of the voter. However, we noticed that there are four types of gender, which are man, woman, non-binary, other, and none and we are more interested in the group of man and woman. Therefore, we filter the gender by using `tidyverse` [@tidyverse]. When the variable `gender` is 1, this indicates "man", but we rename all "man" to "male". When the variable "gender" is 2, it refers to "woman". We also rename all "woman" to "female". Finally, the codebook also define different `race` from 1 to 8, which are White, Black, Hispanic, Asian, Native American, Middle Eastern, Two or more races, and other. We keep all those races because we are not only interested in the major racial group, but also curious about the respond from minority group.
  To better understand the raw data, a summary table @fig-variables had been drawn in order to provide more details for each variables, explaining the variables we select. We select race and gender as the key variables that related to voter behavior. In @fig-vote, we can find the support data for both Biden and Trump based on the variables of gender and race.

## Measurements 
## Measurements 
The collected dataset from the Cooperative Election Study (CES) offers a comprehensive view of U.S. adult citizens' electoral behaviors, political opinions, and demographic characteristics. The CES 2022 dataset, gathered through an online survey by YouGov, encompasses 60,000 instances, meticulously detailed and categorized by various factors such as election experiences, contextual data, demographic information (e.g., gender and race), political affiliations, and opinions on various policy issues. This dataset ensures a reliable representation of the population through its meticulous sampling methodology and validation processes, guaranteeing that it accurately reflects the diverse perspectives within the U.S. electorate. The dataset employs a matched random sampling methodology, with its representativeness further confirmed through a two-stage weighting process involving entropy balancing and iterative proportional fitting. Preprocessing steps, including sample matching, weighting, and vote validation, are conducted to ensure data quality and representativeness, thereby minimizing the risk of representative bias.

@@

In `R` [@citeR], we run a logistic regression model in a Bayesian framework by using the `rstanarm` package of @rstanarm, `here` package of @here and `model_summary` package of @model_summary, we use the default priors from `rstanarm` in order to specific prior probability distributions for each of the parameters in the model. Logistic regression model is used to identify the correlation or relationship between some predictor variables and a outcome variable [@rohan], which is best fit with our research because we aim to identify the relationship between gender and race and support of Biden.

@@

We can use maths by including latex between dollar signs, for instance $\theta$.
## Model justification

@@

From the @tbl-model-summary-tableLogistic, with the constant variable, raceAsian, the intercept is -0.462 which means that the support for Biden decreases by about 0.784 units while all other variables remain the same. The following race, Hispanic (0.354), Middle Eastern (0.535), White (0.940), Native American (1.245), Two or more races (1.372) has stronger/ increasing their support for stronger/ increasing their support for Biden; in this case, the mixed race people have the strongest support for Biden. Yet, Black (−1.030) and Other  (−0.092) decrease support for Biden by looking at the coefficients.
# Discussion {#sec-Discussion}
